---
title: "IB regresion review - comments"
format: html
execute: 
  cache: false
---

investigate comments from ib regression review.

Tasks

Add Phase 1 DTR comparison to Phase 1 HIG 6 DTW
Check HIG P6 vs P5 LIMS recovery modelling
DTR Phase 1 comparison into Mass Recovery model scenarios and see how that trends- MC
P5 HIG 5 and P6 HIG 6 comparison to see significance of choosing P6 as reference - MC
Check phase 1 DTR data to cubist model- 7 rules 53 micron i.e., phase 1 head data, back flagging - MC

To do:

Compare DTR to HIG6 
Compare DTR to HIG5 
Compare HIG5 to HIG6 

Apply cubist rules model to 53 micron data & hig? 

```{r}
library(tidyverse)
library(here)
library(ggstatsplot)

## ggplot theme
theme_mc <- function(base_size = 16) {
    theme_bw(base_size = base_size) %+replace%
        theme(
            # L'ensemble de la figure
            plot.title = element_text(size = rel(1), face = "bold", margin = margin(0, 0, 5, 0), hjust = 0),
            # Zone où se situe le graphique
            panel.grid.minor = element_blank(),
            panel.border = element_blank(),
            # Les axes
            axis.title = element_text(size = rel(0.75), face = "bold"),
            axis.text = element_text(size = rel(0.60), face = "bold"),
            axis.line = element_line(color = "black", arrow = arrow(length = unit(0.3, "lines"), type = "closed")),
            # La légende
            legend.title = element_text(size = rel(0.75), face = "bold"),
            legend.text = element_text(size = rel(0.60), face = "bold"),
            legend.key = element_rect(fill = "transparent", colour = NA),
            legend.key.size = unit(1.5, "lines"),
            legend.background = element_rect(fill = "transparent", colour = NA),
            legend.position = "bottom",
            # Les étiquettes dans le cas d'un facetting
            strip.background = element_rect(fill = "#17252D", color = "#17252D"),
            strip.text = element_text(size = rel(0.75), face = "bold", color = "white", margin = margin(5, 0, 5, 0))
        )
}

theme_set(theme_mc())
```
 
```{r}
# import data

# hig
hig_data <- read_csv(here("data\\DTR_OPF_extraction.csv"))
lims_data <- read_csv(here("data\\LIMS_run.csv"))
dms_data <- read_csv(here("data\\DMS_run.csv"))

MR <- lims_data %>% 
  filter(process_phase == "Mags(calc)") %>% 
  select(hole_id, comp_no, mass_pct) %>% 
  rename(mass_pct_lims = mass_pct) %>% 
  full_join(dms_data %>% filter(process_phase == "DMS Mags") %>% select(hole_id, comp_no, mass_pct) %>% rename(mass_pct_dms = mass_pct), by = c("hole_id","comp_no")) %>% 
  full_join(hig_data %>% filter(type == "DTR Mags"), by = c("hole_id", "comp_no")) %>% 
  mutate(HIG_DTR_MR = ((mass_pct_lims/100)*(mass_pct_dms/100)*(mass_pct/100))*100) %>% 
  select(hole_id, comp_no, HIG_DTR_MR, pass, type)

hig_data <- hig_data %>% 
  full_join(MR, by = c("comp_no", "hole_id", "pass", "type")) %>% 
  full_join(dms_data %>% filter(process_phase == "Calc Head") %>% select(hole_id, comp_no, Fe3O4_pct_SATMAGAN) %>% rename(Fe3O4_pct_head = Fe3O4_pct_SATMAGAN), by = c("hole_id", "comp_no"))

# dtr
dtr_mass <- read_csv(here("data\\dtr_head_mass_rec.csv"))
dtr_assay <- read_csv(here("data\\all_assays_chd.csv"))

dtr_data <- dtr_mass %>%
  select(-c(Fe_pct_XRF, SiO2_pct_XRF)) %>%
  left_join(dtr_assay, by = c("hole_id", "comp_no", "grind_P97"))

dtr_53 <- dtr_data %>%
  filter(grind_P97 == 53)
 
 # hig and dtr 
 
hig_dtr <- dtr_data %>% 
  rename_with(~paste0(., "_dtr"), .cols = grind_P97:FeO_titration) %>% 
  full_join(hig_data, by = c("hole_id", "comp_no"))

## hig5 data 

hig_dtr_p5_cons <- 
  hig_dtr %>% 
  filter(pass == "P5" & type == "DTR Mags", process_phase_dtr == "Cons") %>% 
  select(hole_id, comp_no,process_phase_dtr, grind_P97_dtr, con_mass_rec_pct_dtr, mass_pct, Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_SATMAGAN, Fe_pct_XRF_dtr, Fe_pct_XRF, Fe3O4_pct_head, HIG_DTR_MR) %>% 
  rename(dtr_mass_rec = con_mass_rec_pct_dtr, HIG5_mass_rec = mass_pct, Fe3O4_pct_dtr =Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_HIG5 = Fe3O4_pct_SATMAGAN, Fe_pct_dtr = Fe_pct_XRF_dtr, Fe_pct_HIG5 = Fe_pct_XRF) %>% 
  pivot_longer(cols = c(dtr_mass_rec, HIG_DTR_MR)) %>% 
  rename(dtr_test = name, dtr_value = value) %>% 
  pivot_longer(cols = c(Fe3O4_pct_dtr, Fe3O4_pct_head)) %>% 
  rename(fe3o4_test = name, fe3o4_value = value) %>% 
  pivot_longer(cols = c(Fe_pct_dtr, Fe_pct_HIG5))

hig_dtr_p5_head <- 
  hig_dtr %>% 
  filter(pass == "P5" & type == "Calc Head", process_phase_dtr == "Feed") %>% 
  select(hole_id, comp_no,process_phase_dtr, grind_P97_dtr, con_mass_rec_pct_dtr, mass_pct, Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_SATMAGAN, Fe_pct_XRF_dtr, Fe_pct_XRF, Fe3O4_pct_head, HIG_DTR_MR) %>% 
  rename(dtr_mass_rec = con_mass_rec_pct_dtr, HIG5_mass_rec = mass_pct, Fe3O4_pct_dtr =Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_HIG5 = Fe3O4_pct_SATMAGAN, Fe_pct_dtr = Fe_pct_XRF_dtr, Fe_pct_HIG5 = Fe_pct_XRF) %>% 
  pivot_longer(cols = c(dtr_mass_rec, HIG_DTR_MR)) %>% 
  rename(dtr_test = name, dtr_value = value) %>% 
  pivot_longer(cols = c(Fe3O4_pct_dtr, Fe3O4_pct_head)) %>% 
  rename(fe3o4_test = name, fe3o4_value = value) %>% 
  pivot_longer(cols = c(Fe_pct_dtr, Fe_pct_HIG5))

## hig6 

hig_dtr_p6_cons <- 
  hig_dtr %>% 
  filter(pass == "P6" & type == "DTR Mags", process_phase_dtr == "Cons") %>% 
  select(hole_id, comp_no,process_phase_dtr, grind_P97_dtr, con_mass_rec_pct_dtr, mass_pct, Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_SATMAGAN, Fe_pct_XRF_dtr, Fe_pct_XRF, Fe3O4_pct_head, HIG_DTR_MR) %>% 
  rename(dtr_mass_rec = con_mass_rec_pct_dtr, HIG5_mass_rec = mass_pct, Fe3O4_pct_dtr =Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_HIG5 = Fe3O4_pct_SATMAGAN, Fe_pct_dtr = Fe_pct_XRF_dtr, Fe_pct_HIG5 = Fe_pct_XRF) %>% 
  pivot_longer(cols = c(dtr_mass_rec, HIG_DTR_MR)) %>% 
  rename(dtr_test = name, dtr_value = value) %>% 
  pivot_longer(cols = c(Fe3O4_pct_dtr, Fe3O4_pct_head)) %>% 
  rename(fe3o4_test = name, fe3o4_value = value) %>% 
  pivot_longer(cols = c(Fe_pct_dtr, Fe_pct_HIG5))

hig_dtr_p6_head <- 
  hig_dtr %>% 
  filter(pass == "P6" & type == "Calc Head", process_phase_dtr == "Feed") %>% 
  select(hole_id, comp_no,process_phase_dtr, grind_P97_dtr, con_mass_rec_pct_dtr, mass_pct, Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_SATMAGAN, Fe_pct_XRF_dtr, Fe_pct_XRF, Fe3O4_pct_head, HIG_DTR_MR) %>% 
  rename(dtr_mass_rec = con_mass_rec_pct_dtr, HIG5_mass_rec = mass_pct, Fe3O4_pct_dtr =Fe3O4_pct_SATMAGAN_dtr, Fe3O4_pct_HIG5 = Fe3O4_pct_SATMAGAN, Fe_pct_dtr = Fe_pct_XRF_dtr, Fe_pct_HIG5 = Fe_pct_XRF) %>% 
  pivot_longer(cols = c(dtr_mass_rec, HIG_DTR_MR)) %>% 
  rename(dtr_test = name, dtr_value = value) %>% 
  pivot_longer(cols = c(Fe3O4_pct_dtr, Fe3O4_pct_head)) %>% 
  rename(fe3o4_test = name, fe3o4_value = value) %>% 
  pivot_longer(cols = c(Fe_pct_dtr, Fe_pct_HIG5))
```

# DTR to HIG Comparison 

LIMS Feed is needed to compare properly?

```{r}

## dtr mass recovery

ggbetweenstats(
  hig_dtr_p5_cons %>% filter(grind_P97_dtr == 53),
  x = dtr_test,
  y = dtr_value,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG5 DTW Mass Recovery"
)


ggscatterstats(
  hig_dtr %>% filter(grind_P97_dtr == 53 & pass == "P5" & process_phase_dtr == "Cons" & type == "DTR Mags"),
  x = con_mass_rec_pct_dtr,
  y = HIG_DTR_MR,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG5 DTW Mass Recovery"
) 

## head satmagan

ggbetweenstats(
  hig_dtr_p5_head %>% filter(grind_P97_dtr == 53),
  x = fe3o4_test,
  y = fe3o4_value, 
  title = "Comparison of DTR P97 53 & HIG5 Head Fe3O4 %"
)

ggscatterstats(
  hig_dtr %>% filter(grind_P97_dtr == 53 & pass == "P5" & process_phase_dtr == "Feed" & type == "DTR Mags"),
  x = Fe3O4_pct_SATMAGAN_dtr,
  y = Fe3O4_pct_head,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG5 Fe3O4 %"
)

## fe %

ggbetweenstats(
  hig_dtr_p5_cons %>% filter(grind_P97_dtr == 53),
  x = name,
  y = value, 
  grouping.var = grind_P97_dtr,
  title = "Comparison of DTR P97 53 & HIG5 Con Fe %"
)

ggscatterstats(
  hig_dtr %>% filter(grind_P97_dtr == 53 & pass == "P5" & process_phase_dtr == "Cons" & type == "DTR Mags"),
  x = Fe_pct_XRF_dtr,
  y = Fe_pct_XRF,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG5 Fe %"
) 

```


```{r}

## dtr mass recovery

ggbetweenstats(
  hig_dtr_p6_cons %>% filter(grind_P97_dtr == 53),
  x = dtr_test,
  y = dtr_value,
  xlab = "DTR Test",
  ylab = "Mass Recovery %",
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG6 DTW Mass Recovery"
)

ggscatterstats(
  hig_dtr %>% filter(grind_P97_dtr == 53 & pass == "P6" & process_phase_dtr == "Cons" & type == "DTR Mags"),
  x = con_mass_rec_pct_dtr,
  y = HIG_DTR_MR,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG6 DTW Mass Recovery"
)

## head satmagan

ggbetweenstats(
  hig_dtr_p6_head %>% filter(grind_P97_dtr == 53),
  x = fe3o4_test,
  y = fe3o4_value, 
  ylab = "Head Fe3O4 %",
  xlab = "DTR Test",
  title = "Comparison of DTR P97 53 & HIG6 Head Fe3O4 %"
)

ggscatterstats(
  hig_dtr %>% filter(grind_P97_dtr == 53 & pass == "P6" & process_phase_dtr == "Feed" & type == "DTR Mags"),
  x = Fe3O4_pct_SATMAGAN_dtr,
  y = Fe3O4_pct_head,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG6 Fe3O4 %"
)

## fe %

ggbetweenstats(
  hig_dtr_p6_cons %>% filter(grind_P97_dtr == 53),
  x = name,
  y = value, 
  grouping.var = grind_P97_dtr,
  title = "Comparison of DTR P97 53 & HIG6 Con Fe %"
)

ggscatterstats(
  hig_dtr %>% filter(grind_P97_dtr == 53 & pass == "P6" & process_phase_dtr == "Cons" & type == "DTR Mags"),
  x = Fe_pct_XRF_dtr,
  y = Fe_pct_XRF,
  grouping.var = grind_P97_dtr,
  k = 2,
  title = "Comparison of DTR P97 53 & HIG6 Fe %"
) 
```

# Model Comparison

Compare modelling mass recovery to hig5/6 based on head fe3o4 

```{r}
library(parameters)
library(see)
p5_m <- hig_data %>% 
  filter(type == "DTR Mags" & pass == "P5")

p5_m1 <- lm(HIG_DTR_MR ~ Fe3O4_pct_head, data = p5_m)

p5_m <- hig_data %>% 
  filter(type == "DTR Mags" & pass == "P6")

p6_m1 <- lm(HIG_DTR_MR ~ Fe3O4_pct_head, data = p5_m)

performance::compare_performance(p5_m1, p6_m1)
bind_rows(broom::tidy(p5_m1) %>% mutate(model = "HIG5 MR"), broom::tidy(p6_m1) %>% mutate(model = "HIG6 MR"))
p5_params <- parameters(p5_m1)
p6_params <- parameters(p6_m1)
p5_params$model <- "HIG5 MR"
p6_params$model <- "HIG6 MR"

combined_params <- rbind(p5_params, p6_params)
ggplot(combined_params, aes(x = Parameter, y = Coefficient, color = model)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.2, position = position_dodge(width = 0.5)) +
  labs(title = "Comparison of Coefficients from Different Models",
       y = "Coefficient Estimate",
       x = "Parameter") +
  coord_flip()
```


# HIG5 vs HIG6 

```{r}
library(ggstatsplot)

hig56 <- hig_data %>% 
  filter(pass %in% c("P5", "P6") & type == "DTR Mags") %>% 
  select(HIG_DTR_MR, Fe_pct_XRF, pass) %>% 
  pivot_longer(cols = c(HIG_DTR_MR, Fe_pct_XRF))

ggwithinstats(
  hig56 %>% filter(name == "HIG_DTR_MR"),
  x = pass,
  y = value,
  title = "DTW Mass % HIG P5 to P6",
  ylab = "Mass %"
)

ggwithinstats(
  hig56 %>% filter(name == "Fe_pct_XRF"),
  x = pass,
  y = value,
    title = "Fe Con % HIG P5 to P6",
  ylab = "Fe %"
)

# feed fe3o4 

hig56 <- hig_data %>% 
  filter(pass %in% c("P5", "P6") & type == "Head") %>% 
  select(Fe3O4_pct_SATMAGAN, pass) %>% 
  pivot_longer(cols = c(Fe3O4_pct_SATMAGAN)) 

ggwithinstats(
  hig56,
  x = pass,
  y = value,
    title = "Head Fe3O4 % HIG P5 to P6",
  ylab = "Fe3O4 %"
)
```

# Cubist Model

```{r}
# DTR 

hig_cubist <- dms_data %>% 
  filter(process_phase == "Calc Head") %>% 
  mutate(SCSE_kwh_t = 6.08 + Al2O3_pct_XRF * 0.40 + LOI371_pct * -0.07 * log10(Cr_pct_XRF) * 0.42 + Fe_pct_XRF * 0.25 + Cr_pct_XRF *0.01 + LOI650_pct*0.03 + LOI1000_pct*0.11 + (Al2O3_pct_XRF * LOI371_pct) * -0.20 + (log10(Cr_pct_XRF)*Fe_pct_XRF)*0.05) %>% 
  mutate(bbwi_kwh_t = 15.50+ Al2O3_pct_XRF*0.41+LOI371_pct*0.36+Fe_pct_XRF*-0.01+Cr_pct_XRF*0+CaO_pct_XRF*0.34+(Al2O3_pct_XRF*LOI371_pct)*1.64+(Fe_pct_XRF*Cr_pct_XRF)*0.24+(LOI371_pct*CaO_pct_XRF)*0.98)

cubist_7_hig <- hig_cubist %>%
  mutate(
    result = case_when(
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) > 29.65) ~
        106.9608 - (0.284 * SiO2_pct_XRF) - (0.289 * Fe_pct_XRF) + (59 * Cr_pct_XRF) - (1.09 * K2O_pct_XRF) - (0.68 * SCSE_kwh_t) - (4.2 * Mn_pct_XRF) - (0.92 * MgO_pct_XRF) - (0.197 * bbwi_kwh_t) - (7.5 * TiO2_pct_XRF) - (0.074 * Fe3O4_pct_SATMAGAN) - (4.1 * Na2O_pct_XRF) + (0.02 * Al2O3_pct_XRF),
      
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t > 16.71903) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~
        92.9957 - (29.4 * TiO2_pct_XRF) + (84 * Cr_pct_XRF) - (0.225 * SiO2_pct_XRF) + (0.63 * Al2O3_pct_XRF) - (0.75 * SCSE_kwh_t) - (0.222 * Fe_pct_XRF) - (0.95 * K2O_pct_XRF) - (4.1 * Mn_pct_XRF) - (0.93 * MgO_pct_XRF) + (0.088 * Fe3O4_pct_SATMAGAN) - (5.7 * Na2O_pct_XRF) + (0.133 * bbwi_kwh_t) + (0.9 * S_pct_XRF),
      
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t <= 17.03675) ~
        11.3634 - (10.9 * K2O_pct_XRF) + (1.484 * bbwi_kwh_t) + (1.3 * Al2O3_pct_XRF) + (0.46 * Fe_pct_XRF) + (1.6 * CaO_pct_XRF) + (0.253 * SiO2_pct_XRF) - (12.9 * TiO2_pct_XRF) + (0.122 * Fe3O4_pct_SATMAGAN) + (0.9 * MgO_pct_XRF) - (5.7 * P_pct_XRF) - (1.9 * Mn_pct_XRF) - (17 * Cr_pct_XRF) + (1.2 * S_pct_XRF),
      
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 16.71903) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~
        -18.1729 + (1.953 * bbwi_kwh_t) + (0.883 * Fe_pct_XRF) - (35.5 * TiO2_pct_XRF) + (0.47 * SiO2_pct_XRF) + (0.164 * Fe3O4_pct_SATMAGAN) + (1.45 * MgO_pct_XRF) - (12.3 * Na2O_pct_XRF),
      
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t > 17.03675) ~
        59.9613 + (0.46 * SCSE_kwh_t) - (7.5 * TiO2_pct_XRF) + (0.33 * Al2O3_pct_XRF) + (0.133 * bbwi_kwh_t) - (0.43 * K2O_pct_XRF) + (0.029 * Fe3O4_pct_SATMAGAN) + (0.2 * CaO_pct_XRF) - (10 * Cr_pct_XRF) - (1.6 * Na2O_pct_XRF) - (0.17 * MgO_pct_XRF) - (0.019 * Fe_pct_XRF) - (0.3 * Mn_pct_XRF) + (0.008 * SiO2_pct_XRF),
      
      (K2O_pct_XRF <= 0.053) & (Fe3O4_pct_SATMAGAN <= 15.85) ~
        54.5597 + (1.34 * Al2O3_pct_XRF) + (0.72 * SCSE_kwh_t) - (10.7 * TiO2_pct_XRF) - (0.67 * K2O_pct_XRF) + (0.127 * bbwi_kwh_t) + (0.037 * Fe3O4_pct_SATMAGAN) - (0.32 * MgO_pct_XRF) - (14 * Cr_pct_XRF) - (0.055 * Fe_pct_XRF) - (2.4 * Na2O_pct_XRF) + (0.23 * CaO_pct_XRF) - (0.3 * Mn_pct_XRF),
      
      (bbwi_kwh_t > 21.40164) ~
        97.4764 + (3.11 * Al2O3_pct_XRF) - (68.4 * TiO2_pct_XRF) - (2.51 * SCSE_kwh_t) + (173 * Cr_pct_XRF) - (0.539 * bbwi_kwh_t) + (0.321 * Fe_pct_XRF) - (11.6 * Na2O_pct_XRF) - (0.99 * K2O_pct_XRF),
      
      TRUE ~ NA_real_
    ),
    rule = case_when(
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) > 29.65) ~ 1,
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t > 16.71903) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~ 2,
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t <= 17.03675) ~ 3,
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 16.71903) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~ 4,
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t > 17.03675) ~ 5,
      (K2O_pct_XRF <= 0.053) & (Fe3O4_pct_SATMAGAN <= 15.85) ~ 6,
      (bbwi_kwh_t > 21.40164) ~ 7,
      TRUE ~ NA_integer_
    )
  )

filter_res_dtr <- cubist_7_hig %>% 
  select(rule, result, hole_id, comp_no) %>%
  full_join(hig_data %>% filter(type == "DTR Mags" & pass %in% c("P5", "P6")) %>% select(hole_id, comp_no, Fe_pct_XRF, pass)) 

ggplot(filter_res_dtr) +
  aes(x = result, y = Fe_pct_XRF) +
  geom_point(aes(colour = as.factor(rule))) +
  geom_smooth(method = "lm") +
  geom_abline(lty = 2) +
  tune::coord_obs_pred() +
  facet_wrap(~pass) +
  xlab("Predicted Fe % Con") +
  labs(title = "Cubist 7 Rules: Fe Con % Predicted vs HIG Actuals")


```

## Cubist HIG Data 

```{r}

# HIG Data 

dtr_cubist <- dtr_data %>% 
  mutate(SCSE_kwh_t = 6.08 + Al2O3_pct_XRF * 0.40 + LOI371_pct * -0.07 * log10(Cr_pct_XRF) * 0.42 + Fe_pct_XRF * 0.25 + Cr_pct_XRF *0.01 + LOI650_pct*0.03 + LOI1000_pct*0.11 + (Al2O3_pct_XRF * LOI371_pct) * -0.20 + (log10(Cr_pct_XRF)*Fe_pct_XRF)*0.05) %>% 
  mutate(bbwi_kwh_t = 15.50+ Al2O3_pct_XRF*0.41+LOI371_pct*0.36+Fe_pct_XRF*-0.01+Cr_pct_XRF*0+CaO_pct_XRF*0.34+(Al2O3_pct_XRF*LOI371_pct)*1.64+(Fe_pct_XRF*Cr_pct_XRF)*0.24+(LOI371_pct*CaO_pct_XRF)*0.98)

cubist_7_dtr <- dtr_cubist %>%
  mutate(
    result = case_when(
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) > 29.65) ~
        106.9608 - (0.284 * SiO2_pct_XRF) - (0.289 * Fe_pct_XRF) + (59 * Cr_pct_XRF) - (1.09 * K2O_pct_XRF) - (0.68 * SCSE_kwh_t) - (4.2 * Mn_pct_XRF) - (0.92 * MgO_pct_XRF) - (0.197 * bbwi_kwh_t) - (7.5 * TiO2_pct_XRF) - (0.074 * Fe3O4_pct_SATMAGAN) - (4.1 * Na2O_pct_XRF) + (0.02 * Al2O3_pct_XRF),
      
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t > 16.71903) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~
        92.9957 - (29.4 * TiO2_pct_XRF) + (84 * Cr_pct_XRF) - (0.225 * SiO2_pct_XRF) + (0.63 * Al2O3_pct_XRF) - (0.75 * SCSE_kwh_t) - (0.222 * Fe_pct_XRF) - (0.95 * K2O_pct_XRF) - (4.1 * Mn_pct_XRF) - (0.93 * MgO_pct_XRF) + (0.088 * Fe3O4_pct_SATMAGAN) - (5.7 * Na2O_pct_XRF) + (0.133 * bbwi_kwh_t) + (0.9 * S_pct_XRF),
      
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t <= 17.03675) ~
        11.3634 - (10.9 * K2O_pct_XRF) + (1.484 * bbwi_kwh_t) + (1.3 * Al2O3_pct_XRF) + (0.46 * Fe_pct_XRF) + (1.6 * CaO_pct_XRF) + (0.253 * SiO2_pct_XRF) - (12.9 * TiO2_pct_XRF) + (0.122 * Fe3O4_pct_SATMAGAN) + (0.9 * MgO_pct_XRF) - (5.7 * P_pct_XRF) - (1.9 * Mn_pct_XRF) - (17 * Cr_pct_XRF) + (1.2 * S_pct_XRF),
      
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 16.71903) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~
        -18.1729 + (1.953 * bbwi_kwh_t) + (0.883 * Fe_pct_XRF) - (35.5 * TiO2_pct_XRF) + (0.47 * SiO2_pct_XRF) + (0.164 * Fe3O4_pct_SATMAGAN) + (1.45 * MgO_pct_XRF) - (12.3 * Na2O_pct_XRF),
      
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t > 17.03675) ~
        59.9613 + (0.46 * SCSE_kwh_t) - (7.5 * TiO2_pct_XRF) + (0.33 * Al2O3_pct_XRF) + (0.133 * bbwi_kwh_t) - (0.43 * K2O_pct_XRF) + (0.029 * Fe3O4_pct_SATMAGAN) + (0.2 * CaO_pct_XRF) - (10 * Cr_pct_XRF) - (1.6 * Na2O_pct_XRF) - (0.17 * MgO_pct_XRF) - (0.019 * Fe_pct_XRF) - (0.3 * Mn_pct_XRF) + (0.008 * SiO2_pct_XRF),
      
      (K2O_pct_XRF <= 0.053) & (Fe3O4_pct_SATMAGAN <= 15.85) ~
        54.5597 + (1.34 * Al2O3_pct_XRF) + (0.72 * SCSE_kwh_t) - (10.7 * TiO2_pct_XRF) - (0.67 * K2O_pct_XRF) + (0.127 * bbwi_kwh_t) + (0.037 * Fe3O4_pct_SATMAGAN) - (0.32 * MgO_pct_XRF) - (14 * Cr_pct_XRF) - (0.055 * Fe_pct_XRF) - (2.4 * Na2O_pct_XRF) + (0.23 * CaO_pct_XRF) - (0.3 * Mn_pct_XRF),
      
      (bbwi_kwh_t > 21.40164) ~
        97.4764 + (3.11 * Al2O3_pct_XRF) - (68.4 * TiO2_pct_XRF) - (2.51 * SCSE_kwh_t) + (173 * Cr_pct_XRF) - (0.539 * bbwi_kwh_t) + (0.321 * Fe_pct_XRF) - (11.6 * Na2O_pct_XRF) - (0.99 * K2O_pct_XRF),
      
      TRUE ~ NA_real_
    ),
    rule = case_when(
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) > 29.65) ~ 1,
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t > 16.71903) &
        (bbwi_kwh_t <= 21.40164) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~ 2,
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t <= 17.03675) ~ 3,
      (K2O_pct_XRF > 0.053) &
        (bbwi_kwh_t <= 16.71903) & ((1 * Fe3O4_pct_SATMAGAN + 3) <= 29.65) ~ 4,
      (K2O_pct_XRF <= 0.053) &
        (Fe3O4_pct_SATMAGAN > 15.85) & (bbwi_kwh_t > 17.03675) ~ 5,
      (K2O_pct_XRF <= 0.053) & (Fe3O4_pct_SATMAGAN <= 15.85) ~ 6,
      (bbwi_kwh_t > 21.40164) ~ 7,
      TRUE ~ NA_integer_
    )
  )

filter_res_dtr <- cubist_7_dtr %>% 
  filter(process_phase == "Feed") %>% 
  select(rule, result, grind_P97, hole_id, comp_no) %>%
  full_join(cubist_7_dtr %>% filter(process_phase == "Cons") %>% select(hole_id, comp_no, Fe_pct_XRF)) 

ggplot(filter_res_dtr) +
  aes(x = result, y = Fe_pct_XRF) +
  geom_point(aes(colour = as.factor(rule))) +
  geom_smooth(method = "lm") +
  geom_abline(lty = 2) +
  tune::coord_obs_pred() +
  facet_wrap(~grind_P97) +
  labs(title = "Cubist 7 Rules: Fe Con % Predicted vs DTR Actuals")

```

